%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Vivek Parashar} \\ \vspace{1pt}
    \small +91-9884916300 $|$ \href{mailto:vivekparashar811@gmail.com}{\underline{vivekparashar811@gmail.com}} $|$ 
    \href{https://vivek1052.github.io/}{\underline{https://vivek1052.github.io}}
\end{center}

%-----------Summary--------------
\section{Summary}
  \small{Full-stack Cloud Native Software Engineer with 8 years of experience, ranging from building SaaS ERPs to distributed systems.}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{13th Feb, 2023 -- Present}
      {Shell India Pvt Ltd}{Bengaluru}
      \resumeItemListStart
        \resumeItem{Worked on technical design and development of a blockchain-based book and claim platform for Sustainable Aviation Fuel, Avelia. Used React, NestJS, MongoDB, ether.js, and was deployed on Azure Kubernetes Service using GitHub Actions. Used Mocha \& Jest for unit testing and utilized TTD(Test Driven Development).}
        \resumeItem{Refactored the existing system design to use asynchronous messaging bus instead of REST APIs for microservice-to-microservice communication, which improved scalability and data integrity. Increased volume handling by 10 times from 5 to 49 million gallons, potentially reducing 450,000 tCO2 emissions.}
        \resumeItem{Developed RBAC module to make the platform multi-tenant/multi-persona, enabling the platform to unlock new markets with a 70\% cost and TTM reduction.}
        \resumeItem{Awarded \emph{Continuous Development \& Improvement Award} for refactoring REST APIs with pagination and querying capabilities. 30\% reduction in the creation of new APIs. }
        \resumeItem{Awarded \emph{Innersource Star} award for contributed to open source and in-house capability building by developing libraries such as an OData filter parser and Azure Service Bus wrapper for NestJS.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
   % \resumeSubSubheading
   %  {Software Engineer I}{Oct 2014 - Sep 2016}
   %  \resumeItemListStart
   %     \resumeItem{Apache Beam}
   %       {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
   %  \resumeItemListEnd
   % \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Developer}{1st Apr, 2022 -- 10th Feb, 2023}
      {SAP Labs}{Bengaluru}
      \resumeItemListStart
        \resumeItem{Pioneered a 'Pay per Use' solution using SAP IoT, SAP Subscription Billing and Edge Computing for Industrial IoT challenge. It created billing in based on the usage of a crane mounted on a shipping vessel. Collaborated with cross functions team members for delivery of solution.}
        \resumeItem{Worked on the LLD and development of the Invoice Scanning feature using machine learning to scan physical/digital invoices and create a copy in ByDesign. Reduced the time taken to create an invoice by 50\%.}
        \resumeItem{Took interviews of potential candidates and gave training for product handover to third party vendors.}
    \resumeItemListEnd

    \resumeSubheading
      {Associate Developer}{4th May, 2020 -- 31st Mar, 2022}
      {SAP Labs}{Bengaluru}
      \resumeItemListStart
        \resumeItem{Contributed towards migration of the SaaS ERP product, Business ByDesign, from ABAP to a Node.js-based framework running in a containerized environment using Docker and Kubernetes. Used PostgreSQL as database. Potentially reduced OpEx by 30\% by using cloud service providers such as Alicloud and GCP.}
        \resumeItem{Recognized with \emph{Take It Higher} award for development of a Kanban tool using SAP Capire (a cloud-native development framework), Node.js, and HANA database, which was deployed on SAP Cloud Foundry. Set up a data ingestion pipeline into SAP Analytics Cloud using REST API for reporting purposes.}
        \resumeItem{Gained experience deploying containerized applications using Jenkins CI/CD pipelines. Learned about design patterns and their use within enterprise-grade framework architecture.}
    \resumeItemListEnd

    \resumeSubheading
      {Consultant}{1st Sep, 2019 -- 30th Apr, 2020}
      {Deloitte Consulting USI}{Bengaluru}
      \resumeItemListStart
        \resumeItem{Acted as a full-stack developer for Caterpillar's Transport Unit Monitoring web application using OpenUI5 and OData(REST) APIs. Reduced the lead time for detecting issues in transport units by 40\%. Recognized with \emph{Applause Award}.}
        \resumeItem{Mentored interns on project codebase. }
    \resumeItemListEnd

    \resumeSubheading
      {Business Technology Analyst}{8th Aug, 2016 -- 31st Aug, 2019}
      {Deloitte Consulting USI}{Bengaluru}
      \resumeItemListStart
        \resumeItem{Engineered OData (REST) APIs using SAP Gateway and an SQL database to be consumed by Konica Minolta's E-commerce web application, which was developed using OpenUI5 (a JavaScript framework).}
        \resumeItem{Recognized with \emph{Spot Award} for designing and development of an IDOC monitoring and processing tool using OpenUI5 and OData services.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {VIT University}{Jun 2012 -- May 2016}
      {Bachelor of Technology in Electronics and Communication Engineering}{9.01 CGPA}
  \resumeSubHeadingListEnd
  

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Azure Service Bus Wrapper for NestJS} $|$ \emph{TypeScript, Azure Service Bus, NestJS}}{Nov 2023 -- Dec 2023}
          \resumeItemListStart
            \resumeItem{This is a wrapper library which provides modules for Azure Service Bus package. It allows creating Queues/Controllers using decorators just as Nestjs. Connections are pooled and reused preventing duplicate connections being made to same resource.}
            \resumeItem{\href{https://github.com/vivek1052/azure-service-bus-nestjs-wrapper}{\underline{https://github.com/vivek1052/azure-service-bus-nestjs-wrapper}}}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{OData Filter Parser} $|$ \emph{TypeScript}}{Jun 2023 -- Jul 2023}
          \resumeItemListStart
            \resumeItem{This is a database agnostic library which can be used to parse OData \$filter to a database specific query. Currently it supports MongoDB and SQL.}
           \resumeItem{\href{https://github.com/vivek1052/odata-filter-parser}{\underline{https://github.com/vivek1052/odata-filter-parser}}}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Darpan} $|$ \emph{SAP Capire, CAP CDS, Vue.js, Docker}}{Jul 2021 -- Jun 2022}
          \resumeItemListStart
            \resumeItem{A Photo gallery/manager app written in SAP CAPIRE and Vuejs which can be self hosted as a docker container.}
           \resumeItem{\href{https://github.com/vivek1052/Darpan}{\underline{https://github.com/vivek1052/Darpan}}}
          \resumeItemListEnd

       \resumeProjectHeading
          {\textbf{Portfolio} $|$ \emph{Next.js, Tailwindcss, TypeScript}}{Jul 2021 -- Jun 2022}
          \resumeItemListStart
            \resumeItem{Developer Portfolio website.}
           \resumeItem{\href{https://vivek1052.github.io/}{\underline{https://vivek1052.github.io/}}}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd

%-----------Certifications-----------
\section{Certifications}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Microsoft Certified: Azure Fundamentals}{25th Mar, 2023}
      {Microsoft}{\href{https://www.credly.com/badges/aa9c3ec7-8e5d-4e0f-bd37-19fb382603f8/linked_in_profile}{\underline{Verify}}}

     \resumeSubheading
      {Certified In Cybersecurity}{23rd Aug, 2024}
      {ISC2}{\href{https://www.credly.com/badges/ffbfd08f-225c-435c-aac2-856c6e5c82b7/public_url}{\underline{Verify}}}

    \resumeSubheading
      {LFC131: Green Software for Practitioners}{14th Mar, 2024}
      {Linux Foundation}{\href{https://www.credly.com/badges/92e3361f-275d-44db-9bfd-1c926ea53289/public_url}{\underline{Verify}}}

    \resumeSubheading
      {Open SAP UI5}{28th Jan, 2020}
      {SAP}{}

    \resumeSubheading
      {Software Developer Boot Camp}{Aug 2023}
      {Construx Software}{}
  \resumeSubHeadingListEnd

  
%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: TypeScript, JavaScript, Go, HTML/CSS} \\
     \textbf{Frameworks}{: Node.js, NestJS, React, Express.js, SAP Capire, Mocha, Jest, OpenUI5, Next.js, Vue.js } \\
     \textbf{Developer Tools}{: Git, Docker, Docker-compose, Kubernetes, Github Actions, Terraforms, SonarQube, Mend} \\
     \textbf{Databases}{: MongoDB, Mongoose, PostgreSQL, MySQL, Redis, TypeORM} \\
     \textbf{Protocols}{: REST, Odata, GraphQL, Message Queues, Event-Driven, Pub-Sub, OIDC, Oauth2} \\
     \textbf{System Designs}{: Microservices, Monolith, MVC, Clean architecture, Onion architecture, SaaS, PaaS, IaaS} \\
     \textbf{Cloud Products}{: Azure Kubernetes Service, Azure Service Bus, Azure Key Vault, Azure Blob Storage, Azure WAF, Azure Container Registry, Azure Functions }
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
